Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-03-26 eg6-letters/long-paper/prc-dvcshelium.tex
Update result discussion based on Fucini updated calculation

The asymmetries at 90° are presented in Fig. \ref{fig:IncALU} together with the theoretical
calculation presented also in Fig. \ref{fig:CohALU90}. We observe an important improvement
on the precisision compared to 
the HERMES data, which offers a strong constraint on the model presented. As in the
coherent case, the calculation appears to have issues to reproduce the shape of the data.
However, this time the calculation overshoots the data, sometimes by a significant amount.
An interesting way to look into this issue is to show the result on incoherent DVCS compared 
with the free proton. We can for instance make a ratio, in a fashion similar to the EMC 
effect, which allows to cancel out
the effects from the nucleon structure and highlight nuclear effects. Such ratio is presented
in Fig. \ref{fig:IncRatios}, where we observe again that most models significantly overshoot the data.

@@

This measurement of the incoherent DVCS BSA shows a global tendency of the experimental data 
to be smaller than expected from theoretical calculations. We observe the incoherent DVCS 
BSA to go as low as 60\% of the size of the BSA observed
on the free proton at $x_B \sim 0.15$. This drastic reduction is still unexplained, though some theoretical 
work has been recently published to prolong the calculation from \cite{Fucini:2018gso} to the incoherent 
channel \cite{Fucini:2019xlc}. The explanation for this surprising behavior can come from different sources
both in the initial state and the final state.

Further work is needed to fully comprehend this newly discovered nuclear effect. On the 
experimental side, the use of tagging methods, where the nuclear fragments are measured
appear to offer the best option forward. Indeed, tagging offers the best chance to understand better
this result by offering better control over both the initial and the final state 
effects~\cite{Dupre:2015jha}.

>>>>

The asymmetries at 90° are presented in Fig. \ref{fig:IncALU} together with the theoretical
calculation presented previously in Fig. \ref{fig:CohALU90}. We observe an important improvement
on the precision compared to 
the HERMES data, which offers a strong constraint on the model presented. As in the
coherent case, the calculation appears to have issues to reproduce the shape of the data,
with Fucini {\it et al.}~\cite{Fucini:2019xlc} doing better than the others.
However, this time the calculations overshoot the data, sometimes by a significant amount.

An interesting way to look into this data is to show the result on incoherent nuclear DVCS compared 
with the free proton one. We can for instance make a ratio, in a fashion similar to the EMC 
effect, which allows to cancel out
the effects from the nucleon structure and highlight nuclear effects. Such ratio is presented
in Fig. \ref{fig:IncRatios}.
Notably, the calculation from Fucini {\it et al.}~\cite{Fucini:2019xlc} appears closer to the
others, hinting that maybe the better results with the raw asymmetries was linked to the
input model they used for the free nucleon GPD. Also, they appear to somewhat reproduce the 
shape of the $x_B$ distribution, which would indicate that it is linked to kinematic effects.
Altogether, this result confirms that most models significantly overshoot the data and that 
the BSA in the incoherent DVCS channel is suppressed by 20 to 30 \%.

@@

The explanation for this surprising behavior can come from different sources
both in the initial state and in the final state. 
Further work is needed to fully comprehend this newly discovered nuclear effect. On the 
experimental side, the use of tagging methods, where the nuclear fragments are measured
appear to offer the best option forward. Indeed, tagging offers the best chance to understand better
this result by offering better control over both the initial and the final state 
effects~\cite{Dupre:2015jha}.
